---
title: "Workflow_basics"
author: "Grace B"
date: "22 February 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



4.4 Practice
###1.	Why does this code not work?
```{r}
my_variable <- 10
my_variable
```

 Error in eval(expr, envir, enclos): object 'my_variable' not found
Look carefully! (This may seem like an exercise in pointlessness, but training your brain to notice even the tiniest difference will pay off when programming.)
 my_variable is not found because It is run before assign it to a value 10 . But after assign it a value and running it. It will function properly.
 
###2.	Tweak each of the following R commands so that they run correctly:
library(tidyverse)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

fliter(mpg, cyl = 8)
filter(diamond, carat > 3)

Correct code

```{r}  
		  library(tidyverse)
		  
		  kk<-mpg
		  jj<-diamonds
		  ggplot(data = kk) + 
		    geom_point(mapping = aes(x = displ, y = hwy))
		  
		  filter(kk, cyl == 8)
		  filter(jj, carat > 3)
```


### 3.	Press Alt + Shift + K. What happens? How can you get to the same place using the menus?
#Alt+Shift+K gives keyboard short cuts .
You can get to the same place using tools menu then Key board short cuts.
